Statistical Mechanics Assignment Four

### 2016-05-26 stat_mech/latex/a4.tex
all not done yeat
Add sterrf yadig.
all

@@

>>>>

\section{Problem One: Thermodynamics problem}
Here we are solving for the behavior of a fairly simple thermodynamic system.\\

\textbf{a.) Final pressure}

\begin{align*}
  \bar{p}V' &= \nu RT\\
  p_f &= \frac{\nu_f RT}{V_f} = \frac{2\nu RT}{V'(1+b)}\\
  &= \frac{2\nu RT\bar{p}}{(1+b)\nu RT} = \frac{2\bar{p}}{1+b}\\
\end{align*}

@@

\section{Problem Three: Restoring-force systems}

\textbf{a.) Linear restoring force}
\begin{align*}
  Z = \int_0^\infty e^{-\alpha x^2/2kT}dx\\
  &= \left(\frac{2\pi kT}{\alpha}\right)^{1/2}\\
  <E>_r &= \frac{N}{Z}\int_0^\infty \frac{\alpha x^2}{2}
  &= \frac{NkT}{2}\\
  <E> &= <E>_{ideal} + <E>_r = NkT\\
\end{align*}

\textbf{b.) Cubic restoring force}
\begin{align*}
  Z &= \int_{-\infty}^{\infty}e^{\alpha x^4/4kT}
  = \frac{1}{2}\left(\frac{4kT}{\alpha}\right)^{1/4}\Gamma\left(\frac{1}{4}\right)\\
  <E> &= 2N\left(\frac{\alpha}{4kT}\right)^{1/4}\Gamma\left(\frac{1}{4}\right)^{-1}
  \int_{-\infty}^\infty \frac{\alpha x^4}{4}e^{-\alpha x^4 / 4kT}\\
\end{align*}

\textbf{b.) Cubic restoring force}
\begin{align*}
  Z &= \int_{-\infty}^{\infty}e^{\alpha x^4/4kT}
  = \frac{1}{2}\left(\frac{\alpha}{4kT}\right)^{1/4}\Gamma\left(\frac{1}{4}\right)\\
  <E> &= N\sum E_ip_i =
  2N\left(\frac{\alpha}{4kT}\right)^{1/4}\Gamma\left(\frac{1}{4}\right)^{-1}
  \int_{-\infty}^{\infty}\frac{\alpha x^4}{4}e^{\alpha x^4/4kT}\\
  &= \frac{N\alpha}{2}\left(\frac{\alpha}{4kT}\right)^{1/4}\Gamma\left(\frac{1}{4}\right)^{-1}
  \frac{5}{16}\left(\frac{2kT}{\alpha}\right)\left(\frac{2kT}{\alpha}\right)^{1/4}
  \Gamma\left(\frac{1}{4}\right)\\
  &= N\alpha\left(\frac{\alpha}{4kT}\right)^{1/4}
  \frac{5}{16}\left(\frac{4kT}{\alpha}\right)\left(\frac{4kT}{\alpha}\right)^{1/4}\\
  &= \frac{5}{4}NkT\\
\end{align*}
